Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases

### 2021-07-13 submission/submission.tex
prepare subsection for sudoku code
minor changes

\author{OCamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote}}
\title{Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases}

@@

@@

>>>>

\author{OCamlPro - Fabrice Le Fessant\footnote{Telegram: @fabrice\_dune} and Thomas Sibut-Pinote\footnote{Telegram: @ThomasSibutPinote} \\ \small{\url{https://github.com/OCamlPro/devex-18-zk-contest}}}
\title{Groth16 zk-SNARK Proof Verification on Freeton : Three Use Cases}
\date{}

@@

\emph{Note: You may skip this section if you don't want to focus too much on the details on a first reading.}

@@

\subsection{Code}
\label{subsec:sudoku_code}

TODO: code du sudoku ici
